How Safe is Campas Really? Assault Rate Trends Within and Around the University of Toronto: A Ten-Year Analysis

### 2024-01-24 outputs/paper/paper.qmd
made a couple naming changes.

long_data <- cleaned_data |>
  gather(key = "Year", value = "Assault_Rate", -Neighbourhood) |>
  mutate(Year = as.numeric(str_replace(Year, "ASSAULT_RATE_", "")))

# Plot the graph
ggplot(long_data, aes(x = Year, y = Assault_Rate, group = Neighbourhood, color = Neighbourhood)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Assault Rates in University of Toronto 
      Neighbourhoods (2014-2023)",
    x = "Year",
    y = "Assault Rate",
    color = "Neighbourhood"
  ) +
  ylim(0, 5000) # Adjust these values based on your data's range

@@

long_data <- surrounding_neighbourhoods |>
  gather(key = "Year", value = "Assault_Rate", -Neighbourhood) |>
  mutate(Year = as.numeric(str_extract(Year, "\\d{4}")))

@@

# Your data preparation code
long_data <- all_neighbourhoods |>
  gather(key = "Year", value = "Assault_Rate", -Neighbourhood) |>
  mutate(Year = as.numeric(str_extract(Year, "\\d{4}")))

# Plot the graph with facets and without a legend
ggplot(long_data, aes(x = Year, y = Assault_Rate, group = Neighbourhood, color = Neighbourhood)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Assault Rates in University of Toronto's Surrounding Neighbourhoods (2014-2023)",
    x = "Year",
    y = "Assault Rate"
  ) +
  scale_x_continuous(breaks = seq(from = 2014, to = 2023, by = 1)) +
  facet_wrap(~ Neighbourhood, scales = "free_x") +
  theme(
    legend.position = "none", # This line removes the legend
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
  )

@@

There are potential measurment errors in the dataset used for this analysis. The dataset might not capture all incidents, as not all assaults are reported. Factors such as the victim's willingness to report, trust in campus authorities, and awareness of reporting channels can influence the data. Perhaps trust in campus authorities and awareness of the importance to report is strong on campus and therefore more assaults are reported in these neighbourhoods.

>>>>

assault_data <- cleaned_data |>
  gather(key = "Year", value = "Assault_Rate", -Neighbourhood) |>
  mutate(Year = as.numeric(str_replace(Year, "ASSAULT_RATE_", "")))

# Plot the graph
ggplot(long_data, aes(x = Year, y = Assault_Rate, group = Neighbourhood, color = Neighbourhood)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Assault Rates in University of Toronto 
      Neighbourhoods (2014-2023)",
    x = "Year",
    y = "Assault Rate",
    color = "Neighbourhood"
  ) +
  ylim(0, 3000) # Adjust these values based on your data's range

@@

asst_data <- surrounding_neighbourhoods |>
  gather(key = "Year", value = "Assault_Rate", -Neighbourhood) |>
  mutate(Year = as.numeric(str_extract(Year, "\\d{4}")))

@@

# My data prep
long_data <- all_neighbourhoods |>
  gather(key = "Year", value = "Assault_Rate", -Neighbourhood) |>
  mutate(Year = as.numeric(str_extract(Year, "\\d{4}")))

# Plot the graph with facets and without a legend because legend was to big and messy and every facet is already labelled nicely
ggplot(long_data, aes(x = Year, y = Assault_Rate, group = Neighbourhood, color = Neighbourhood)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Assault Rates in University of Toronto's Surrounding Neighbourhoods (2014-2023)",
    x = "Year",
    y = "Assault Rate"
  ) +
  scale_x_continuous(breaks = seq(from = 2014, to = 2023, by = 1)) +
  facet_wrap(~ Neighbourhood, scales = "free_x") +
  theme(
    legend.position = "none", # This line removes the legend
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)
  )

@@

There are potential measurement errors in the dataset used for this analysis. The dataset might not capture all incidents, as not all assaults are reported. Factors such as the victim's willingness to report, trust in campus authorities, and awareness of reporting channels can influence the data. Perhaps trust in campus authorities and awareness of the importance to report is strong on campus and therefore more assaults are reported in these neighbourhoods.
